Polynomial phase estimation by phase unwrapping

### 2012-10-18 paper.tex
more edits to paper.

An interesting property is that the estimator of the $k$th polynomial phase coefficient converges almost surely to $\tilde{\mu}_k$ at rate $N^{-k}$.  This is perhaps not surprising, since it is the same rate observed in polynomial regression.  However, asserting that convergence at this rate occurs in the polynomial phase setting is not trivial.  For this purpose we make use of an elementary result about the number of arithmetic progressions contained inside subsets of $\{1,2,\dots,N\}$.  %This proof technique appears to be novel, and may be useful in other problems.  
The proof of asymptotic normality is complicated by the fact that the objective function corresponding with the LSU estimator is not differentiable everywhere.  Techniques developed by Huber~\cite{Huberrobustest1964,Huberbehavmaxnonstandard1967} and Pollard~\cite{Pollard_new_ways_clts_1986,Pollard_asymp_empi_proc_1989} and results from the literature on hyperplane arrangements~\cite{Chazelle_discrepency_method_2000,Matousek_lect_disc_geom_2002} become useful here.  We are hopeful that the proof techniques developed here will be useful for purposes other than polynomial phase estimation, and in particular other applications involving data that is `wrapped' in some sense.  Potential candidates are the phase wrapped images observed in modern radar and medical imaging devices such as synthetic aperture radar and magnetic resonance imaging~\cite{Nico_phaseunwrappingSAR_2000}.

>>>>

An interesting property is that the estimator of the $k$th polynomial phase coefficient converges almost surely to $\tilde{\mu}_k$ at rate $N^{-k}$.  This is perhaps not surprising, since it is the same rate observed in polynomial regression.  However, asserting that convergence at this rate occurs in the polynomial phase setting is not trivial.  For this purpose we make use of an elementary result about the number of arithmetic progressions contained inside subsets of $\{1,2,\dots,N\}$.  %This proof technique appears to be novel, and may be useful in other problems.  
The proof of asymptotic normality is complicated by the fact that the objective function corresponding with the LSU estimator is not differentiable everywhere.  Techniques developed by Huber~\cite{Huberrobustest1964,Huberbehavmaxnonstandard1967} and Pollard~\cite{Pollard_new_ways_clts_1986,Pollard_asymp_empi_proc_1989} and results from the literature on hyperplane arrangements~\cite{Chazelle_discrepency_method_2000,Matousek_lect_disc_geom_2002} become useful here.  We are hopeful that the proof techniques developed here will be useful for purposes other than polynomial phase estimation, and in particular other applications involving data that is `wrapped' in some sense.  Potential candidates are the phase wrapped images observed in modern radar and medical imaging devices such as synthetic aperture radar and magnetic resonance imaging~\cite{Nico_phaseunwrappingSAR_2000,Friedlander_PD_phaseunwrapping_1996}.
